%!TEX root = ../main.tex

\begin{coverpage}{Acknowledgements}
First of all, I would like to thank Professor Fred A. Hamprecht, for sparking my passion for Machine Learning through his lectures and accompanying projects. 
As my supervisor, he provided me with the resources and support to develop and explore my ideas and develop myself as a scientist. I enjoyed our intense and productive discussions, where he always challenged me to dig deeper. I am incredibly grateful for the pleasant environment that he procures, full of incredibly friendly, supportive, and intelligent people that made collaborating a pure joy. 

I especially want to thank Constantin Pape and Alberto Bailoni, who played an indispensable role in conceiving and understanding the Mutex Watershed. In this spirit, I also want to thank Lukas Schott and Yuyan Li for working so closely together with me and push the Watershed algorithms to their limits. I would also like to thank the senior group members Ullrich Köthe, Anna Kreshuk, Carsten Hauboldt, and Martin Schiegg for the guidance and helping me to get up on my science feet. In particular, I like to thank Ullrich Köthe for our in-depth discussions about image segmentation algorithms and his late-night support during my first paper.
I would also like to thank Jan Funke, who invited me to visit his group in Janelia, explored new ideas with me, and encouraged me to think about the bigger picture. I fondly remember the friendly atmosphere and intelligent discussions in his group that immediately made me feel at home. I also want to thank my close friend Stefan Richter who was always reliable in planing our eventing, but most importantly, as a supporter during stressful times. A special thanks goes to Barbara Werner for fighting our bureaucratic battles. I would also like to thank my official supervisor Carsten Rother for his interest in my project and valuable comments during my presentations.
Finally, I would like to thank Luka Smalinskaite for her love, support, and simply making my life better. Special thanks, of course, also goes to my parents for their continuous, unconditional support throughout my life.


----

First, I like to thank Professor Fred Hamprecht for being the Supervisor for this thesis. I have been working in his research group Image Analysis and Learning for almost a decade. Since I joined the group as bachelor student, it has always been a pleasure to collaborate with so many friendly, intelligent and helpful people. I like to thank Bjoern Andres and Jörg Kappes for introducing me to the field of discrete optimization and many hours of fruitful discussions about algorithms and software. I like to thank Ullrich Köthe for many fruitful discussion about image segmentation, algorithms and software in general. I like to thank Thorben Kroeger, Niko Krasowki, Anna Kreshuk and Constantin Pape for our strong collaboration and joint work on automatic segmentation for 3D-EM Data. In particular I like to thank Constantin Pape for the many hours of work he invested in joint research papers and software projects. I had many enjoyable moments with Christoph Straehle and Luca Fiasch and Sven Wanner outside of the building. I enjoyed the special humor of Philipp Hanslovsky and Robert Walecki very much. I enjoyed many cups of coffees with Steffen Wolf, Lorenzo Cerrone, Constantin Pape, Phillip Schmidt, Peter Neigel, Christoph Straehle, Nasim Rahaman and Anna Kreshuk where we hand many enjoyable discussions. A special thanks to Barbara Werner for all her incredible work.

\end{coverpage}
