%!TEX root = ../main.tex


\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications} 

I contributed to the following peer reviewed publications:

\begin{itemize}
\item \textbf{Alberto Bailoni}\footnote{Both authors contributed equally\label{note1}}, Steffen Wolf\cref{note1}, Constantin Pape, Nasim Rahaman, Anna Kreshuk, Ullrich K\"othe, and Fred A. Hamprecht. ``The Mutex Watershed and Its Objective: Efficient, Parameter-Free Image Partitioning.'' In: \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence (PAMI)}. 2020.
\item \textbf{Alberto Bailoni}, Constantin Pape, Steffen Wolf, Anna Kreshuk, and Fred A. Hamprecht. ``Proposal-free volumetric instance segmentation from latent single-instance masks.'' In: \emph{ German Conference on Pattern Recognition (GCPR)}. 2020.
\item Steffen Wolf, Constantin Pape, \textbf{Alberto Bailoni}, Nasim Rahaman, Anna Kreshuk, Ullrich Kothe, and Fred A. Hamprecht. ``The mutex watershed: efficient, parameter-free image partitioning.'' In: \emph{Proceedings of the European Conference on Computer Vision (ECCV)}. 2018.
\item Elke Kirschbaum, \textbf{Alberto Bailoni}, and Fred A. Hamprecht. ``DISCo: Deep learning, Instance Segmentation, and Correlations for cell segmentation in calcium imaging''. In: \emph{International Conference on Medical Image Computing and Computer-Assisted Intervention (ISBI)}. 2020.
\item Steffen Wolf, Yuyan Li, Constantin Pape, \textbf{Alberto Bailoni}, Anna Kreshuk, and Fred A. Hamprecht. ``The Semantic Mutex Watershed for Efficient Bottom-Up Semantic Instance Segmentation.'' In: \emph{Proceedings of the European Conference on Computer Vision (ECCV)} (2020).
\item Adrian Wolny, Lorenzo Cerrone, Athul Vijayan, Rachele Tofanelli, Amaya Vilches Barro, Marion Louveaux, Christian Wenzl, S\"oren Strauss, David Wilson-S\'anchez, Rena Lymbouridou, Susanne S Steigleder, Constantin Pape, \textbf{Alberto Bailoni}, Salva Duran-Nebreda, George W Bassel, Jan U Lohmann, Miltos Tsiantis, Fred A Hamprecht, Kay Schneitz, Alexis Maizel, and Anna Kreshuk. ``Accurate and versatile 3D segmentation of plant tissues at cellular resolution''. In: \emph{Elife, 9, e57613.} 2020.
\end{itemize}

\noindent The following publications are currently under peer review:
\begin{itemize}
\item \textbf{Alberto Bailoni}, Constantin Pape, Steffen Wolf, Thorsten Beier, Anna Kreshuk, and Fred A. Hamprecht. ``A Generalized Framework for Agglomerative Clustering of Signed Graphs applied to Instance Segmentation''. \emph{arXiv preprint arXiv:1906.11713.} (2021)
\end{itemize}
